Arc Blanc: a real time ocean simulation framework

### 2025-03-04 paper.tex
Use a compress version of the images

\begin{figure}[h]
	\centering
    \includegraphics[width=4in]{Figures/experiment1-contrast.png}
    \caption{Example of rendering of \framework.}
    \label{fig:teaser}
\end{figure}

@@

	\subfloat[Using $\delta = 0$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion0SeaState5-contrast.png}
		\label{fig:dispersion0}
	}
	\hfill
	\subfloat[Using $\delta = 1$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion1SeaState5-contrast.png}
		\label{fig:dispersion1}
	}
	\caption{Effect of the parameter $\delta$ on sea state $5$ on the Beaufort scale.}
	\label{fig:dispersionEffect}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\subfloat{\includegraphics[width=0.7\textwidth]{Figures/gridInterpolationDegree8.png}\label{fig:gridInterpolationDegee8}}
	\hfill
	\subfloat{\includegraphics[width=0.3\textwidth]{Figures/gridInterpolationDegree8Legend.png}\label{fig:gridInterpolationDegree8Legend}}
	\caption{This figure shows a comparison between a \textcolor{bleuF}{uniform discretization in blue} and a \textcolor{redF}{logarithmic discretization in red}. The dotted parts represent the last interpolation toward a null velocity at $y_{min}$.}
	\label{fig:comparisonGrid}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/interpolationAccuracyComparisonLogScale.png}\label{subfig:interpolationAccuracyComparisonLogScale}
	\caption{This figure represents the accuracy of different type of interpolation in function of the size of the discretization $N$. The accuracy axis used a logarithmic scale to be more readable.
		It uses 10000 positions from a continuous uniform distribution in the parallelepiped $[-1000,1000]\times[-125,4.5]\times[-1000, 1000]$ and with a wind speed of 20 $m.s^{-1}$.
		The interpolated velocity $\tilde{\mathbf{v}}$ and the analytical velocity $\mathbf{v}$ are evaluated.
		The accuracy is defined by the mean of all positions of $\big|||\tilde{\mathbf{v}}||-||\mathbf{v}||\big|$.
		It can be noticed that considering a uniform discretization, then exponential interpolation has a better accuracy than linear one.
		Logarithmic discretization is much better than uniform discretization, whatever the used interpolation.
		At least, for low $N$, exponential interpolation gives slightly better result than linear interpolation.}
	\label{fig:interpolationAccuracyComparison}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/interpolationMeanPerformancesAndAccuracy.png}
	\caption{These figures represent the different objective for choosing the interpolation degree. In blue, the mean accuracy of velocity interpolation in meters per seconds, we denote this function $A(d)$. In red, the mean performances of velocity interpolation in deciseconds, we denote this function $P(d)$. We estimate this function with $10000$ sample.}
	\label{fig:interpolationCriteria}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/multiObjectiveAccuracy1Duration2.png}
	\caption{Multi-objective function $P$ to optimize, with two objectives: performance and accuracy.
		Its minimum is reached by the interpolation degree of $8$. For more details on each objective, see Figures \ref{fig:interpolationCriteria} which represent them individually.}
	\label{fig:multiObjectiveFunction}
\end{figure}

@@

	\subfloat[Three quarter view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_diagonal_view.png}
	}
	\hspace{1cm}
	\subfloat[Back view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_back_view.png}
	}
	\hspace{1cm}
	\subfloat[Side view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_side_view.png}
	}
	\caption{Three different theoretical point of view of the mask for a simple rectangle.}
	\label{fig:mask_maskTheoreticalView}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\subfloat[The height of the mask of a simple boat encoded in a single channel texture.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/MaskHeightMap.png}
		\label{subfig:maskHeightMap}
	}
	\hspace{1cm}
	\subfloat[The height of the mask of a simple boat in a 3D scene with a very low sea state. Boat rendering and wave propagation has been disabled to only display the initial step of the height of the mask.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/Mask3D-contrast.png}
		\label{subfig:mask3D}
	}
	\caption{Two different views of the height of the mask defined by Equation \ref{equa:mask_full} for a simple boat.}
	\label{fig:mask}
\end{figure}

@@

	\subfloat[\emph{One-solid} using sea state $1$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/experiment1-1-contrast.png}
		\label{fig:experiment1-1}
	}
	\hspace{1cm}
	\subfloat[\emph{One-solid} using sea state $6$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/experiment1-2-contrast.png}
		\label{fig:experiment1-2}
	}
	\vspace{1cm}
	\subfloat[\emph{Ten-solids} using sea state $1$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/experiment2-contrast.png}
		\label{fig:experiment2-1}
	}
	\hspace{1cm}
	\subfloat[\emph{Ten-solids} using sea state $4$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/experiment2-3-contrast.png}
		\label{fig:experiment2-2}
	}
	\caption{The two experiments with different sea state: \emph{one-solid} on top row, and \emph{ten-solids} on bottom one.}
	\label{fig:experiments}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\textwidth]{Figures/results_cm.png}
	\caption{Mean number of steps required for convergence as a function of wind speed. Error bars represent the variance of iterations across $1000$ test points.}
	\label{fig:convergence_steps}
\end{figure}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\textwidth]{Figures/resultsExecutionTime.png}
	\caption{Average execution time per iteration count over $1000$ tests, measured across $10^5$ sample positions. Error bars indicate variance in execution time.}
	\label{fig:execution_time}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
    \includegraphics[width=4in]{Figures/experiment1-contrast.jpg}
    \caption{Example of rendering of \framework.}
    \label{fig:teaser}
\end{figure}

@@

	\subfloat[Using $\delta = 0$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion0SeaState5-contrast.jpg}
		\label{fig:dispersion0}
	}
	\hfill
	\subfloat[Using $\delta = 1$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion1SeaState5-contrast.jpg}
		\label{fig:dispersion1}
	}
	\caption{Effect of the parameter $\delta$ on sea state $5$ on the Beaufort scale.}
	\label{fig:dispersionEffect}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\subfloat{\includegraphics[width=0.7\textwidth]{Figures/gridInterpolationDegree8.jpg}\label{fig:gridInterpolationDegee8}}
	\hfill
	\subfloat{\includegraphics[width=0.3\textwidth]{Figures/gridInterpolationDegree8Legend.jpg}\label{fig:gridInterpolationDegree8Legend}}
	\caption{This figure shows a comparison between a \textcolor{bleuF}{uniform discretization in blue} and a \textcolor{redF}{logarithmic discretization in red}. The dotted parts represent the last interpolation toward a null velocity at $y_{min}$.}
	\label{fig:comparisonGrid}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/interpolationAccuracyComparisonLogScale.jpg}\label{subfig:interpolationAccuracyComparisonLogScale}
	\caption{This figure represents the accuracy of different type of interpolation in function of the size of the discretization $N$. The accuracy axis used a logarithmic scale to be more readable.
		It uses 10000 positions from a continuous uniform distribution in the parallelepiped $[-1000,1000]\times[-125,4.5]\times[-1000, 1000]$ and with a wind speed of 20 $m.s^{-1}$.
		The interpolated velocity $\tilde{\mathbf{v}}$ and the analytical velocity $\mathbf{v}$ are evaluated.
		The accuracy is defined by the mean of all positions of $\big|||\tilde{\mathbf{v}}||-||\mathbf{v}||\big|$.
		It can be noticed that considering a uniform discretization, then exponential interpolation has a better accuracy than linear one.
		Logarithmic discretization is much better than uniform discretization, whatever the used interpolation.
		At least, for low $N$, exponential interpolation gives slightly better result than linear interpolation.}
	\label{fig:interpolationAccuracyComparison}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/interpolationMeanPerformancesAndAccuracy.jpg}
	\caption{These figures represent the different objective for choosing the interpolation degree. In blue, the mean accuracy of velocity interpolation in meters per seconds, we denote this function $A(d)$. In red, the mean performances of velocity interpolation in deciseconds, we denote this function $P(d)$. We estimate this function with $10000$ sample.}
	\label{fig:interpolationCriteria}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/multiObjectiveAccuracy1Duration2.jpg}
	\caption{Multi-objective function $P$ to optimize, with two objectives: performance and accuracy.
		Its minimum is reached by the interpolation degree of $8$. For more details on each objective, see Figures \ref{fig:interpolationCriteria} which represent them individually.}
	\label{fig:multiObjectiveFunction}
\end{figure}

@@

	\subfloat[Three quarter view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_diagonal_view.jpg}
	}
	\hspace{1cm}
	\subfloat[Back view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_back_view.jpg}
	}
	\hspace{1cm}
	\subfloat[Side view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_side_view.jpg}
	}
	\caption{Three different theoretical point of view of the mask for a simple rectangle.}
	\label{fig:mask_maskTheoreticalView}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\subfloat[The height of the mask of a simple boat encoded in a single channel texture.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/MaskHeightMap.jpg}
		\label{subfig:maskHeightMap}
	}
	\hspace{1cm}
	\subfloat[The height of the mask of a simple boat in a 3D scene with a very low sea state. Boat rendering and wave propagation has been disabled to only display the initial step of the height of the mask.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/Mask3D-contrast.jpg}
		\label{subfig:mask3D}
	}
	\caption{Two different views of the height of the mask defined by Equation \ref{equa:mask_full} for a simple boat.}
	\label{fig:mask}
\end{figure}

@@

	\subfloat[\emph{One-solid} using sea state $1$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/experiment1-1-contrast.jpg}
		\label{fig:experiment1-1}
	}
	\hspace{1cm}
	\subfloat[\emph{One-solid} using sea state $6$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/experiment1-2-contrast.jpg}
		\label{fig:experiment1-2}
	}
	\vspace{1cm}
	\subfloat[\emph{Ten-solids} using sea state $1$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/experiment2-contrast.jpg}
		\label{fig:experiment2-1}
	}
	\hspace{1cm}
	\subfloat[\emph{Ten-solids} using sea state $4$.]
	{
		\includegraphics[width=0.4\textwidth]{Figures/experiment2-3-contrast.jpg}
		\label{fig:experiment2-2}
	}
	\caption{The two experiments with different sea state: \emph{one-solid} on top row, and \emph{ten-solids} on bottom one.}
	\label{fig:experiments}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\textwidth]{Figures/results_cm.jpg}
	\caption{Mean number of steps required for convergence as a function of wind speed. Error bars represent the variance of iterations across $1000$ test points.}
	\label{fig:convergence_steps}
\end{figure}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\textwidth]{Figures/resultsExecutionTime.jpg}
	\caption{Average execution time per iteration count over $1000$ tests, measured across $10^5$ sample positions. Error bars indicate variance in execution time.}
	\label{fig:execution_time}
\end{figure}
